Millions of Type Errors

### 2023-09-12 programming23/paper.tex
Tidying up
Tidying up telemetry intro

The state of the world in a {Roblox} experience is captured by
the \emph{data model}, which is a tree of \emph{instances}, such as
parts, models, meshes, effects, lighting, audio assets, and physics
constraints such as forces, springs and joints.

While an experience is under development, it is typical for the data
model to be edited (for example instances to be added, deleted, moved
or renamed). Since the initial shape of the data model tree is reflected in
the type system, it is possible for these edits to introduce type errors.

@@

Prior work: transparent telemetry, VS Code telemetry, many others undocumented
that are probably not cleary documented.
\Cref{t:telemetry-design} gives an overview.

\paragraph{Goals:}

\begin{itemize}
  \item
    Learn about type system adoption and use
  \item
    Discover roadblocks to adoption
  \item
    Assess the helpfulness of error highlights
\end{itemize}

\paragraph{Limits:}

\begin{itemize}
\item
  No personal data (PII)
  \subitem
    Fairly obvious.
    But, we also can't collect directory names, filenames, or code snapshots
    because these all might have PII throughout.
\item
  No data about public events.
  \subitem
    Contributions to the Roblox Marketplace, for instance, are a public event.
    Although it would be interesting to know the number of type errors
    in published experiences, this data might be used to identify creators
    who publish often --- or on a distinct schedule.
\item
  Low cost
  \subitem
    Building, sending, and storing the data must all run quickly.
    FILL what was our hard cap on Kibana use?
\end{itemize}

\paragraph{Solutions:}

@@

Extra Roblox constraints:
- No access to some events: save, exit
- No idea if analysis widget is open, closed, or obscured
- Don't know which module is the data model
  (no ids for ANY module for that matter)

\url{https://docs.google.com/document/d/1DnKvw8x1jy0EWCbBSM8neKULWz7WAg1OauKy7qqYqkI/edit}

\subsection{What are we logging (from gdoc)}

>>>>

The state of the world in a {Roblox} experience is captured by
the \emph{data model}, which is a tree of \emph{instances}, such as
parts, models, meshes, effects, lighting, audio assets, and physics
constraints such as forces, springs and joints.
The data model can be seen in the Explorer view of Fig.~\ref{fig:roblox-studio}.
While an experience is under development, it is typical for the data
model to be edited (for example instances to be added, deleted, moved
or renamed). Since the initial shape of the data model tree is reflected in
the type system, it is possible for these edits to introduce type errors.

@@

\subsection{Limits of telemetry}

Telemetry allows an application to ``phone home'' with data
summarizing usage patterns, such performance data, crash reporting,
and feature uptake. A typical usage is in deciding whether an API can
be deprecated: without telemetry it may be difficult to know how
popular a feature is with users, but with telemetry it is
straightforward.

IDEs use telemetry in a similar fashion to most user-facing
applications, for example VSCode~\cite{vsc-telemetry} and
IntelliJ~\cite{intellij-telemetry} report telemetry.

Telemetry for programming languages can be controversial, for example
the lively discussion around telemetry in the Go
toolchain~\cite{golang-telemetry}. 
The Luau open source toolchain does \emph{not} report telemetry,
as it is designed to be used in build environments such as Continuous Integration
servers, where hermetic deterministic builds are expected.

Much of the concern about telemetry is because of its potential impact on
privacy, by revealing Personally Identifiable Information (PII).
For this reason, it is important that any experiments using telemetry
not reveal PII:
no source code;
no source code locations;
no error messages (which may contain source code);
no record of the creator's identity, locale, or IP address;
and no information about what creation the data came from.
A good introduction to the privacy implications and tradeoffs
involved with telemetry is~\cite{transparent-telemetry}.

For performance reasons, there are limits to telemetry data:
telemetry records have size limits, and the performance impact of
recording telemetry should be minimal.

In summary, the limitations of telemetry are:
\begin{itemize}
  \item Data which reveals no PII.
  \item Fixed-size telemetry records.
  \item Minimal overhead to record telemtry.
\end{itemize}
In addition, due to the architecture of Roblox Studio
there is some information that is not available to the
typechecker:
\begin{itemize}
  \item The typechecker does not have access to some lifecycle events,
    such as save, quit and publish.
  \item The typechecker does not have access to GUI state, for example
    whether the Script Analysis widget is visible.
\end{itemize}

\subsection{When are we logging?}

@@

\subsection{What are we logging?}
